---
title: "Dual Bellows efficiency"
output:
  html_document:
    df_print: paged
---

Figure out Anne's "efficiency" before and after single shot stds.


```{r}
library(amstools)
library(odbc)
library(amstools)
library(tidyverse)
```
# Total efficiency

Anne's efficiency on the dual bellows line per day and per running day.

Anne's gf_operator_id is 70, and the db reactors are 41-50 and 410-500.

```{r}
# efficiency function by total days
eff <- function(data) {
  nrow(data) / as.numeric(max(data$gf_date) - min(data$gf_date))
}

# efficiency by run days
effrd <- function(data) {
  nrow(data) / length(unique(data$gf_date))
}

effdate <- function(from, to) {
  
  con <- conNOSAMS()
  sql <- "SELECT * 
         FROM graphite 
         WHERE gf_operator_id = 70
         AND gf_date BETWEEN ? AND ?
         AND (gf_reactor BETWEEN 410 AND 500
         OR gf_reactor BETWEEN 41 AND 50)"
  query <- odbc::dbSendQuery(con, sql)
  odbc::dbBind(query, list(from, to))
  data <- odbc::dbFetch(query)
  odbc::dbClearResult(query)
  
  list(eff(data),  
       effrd(data))  
}
```

### Before switch to single-shot standards

```{r}
e <- effdate("2017-01-01", "2018-05-01")
```

Efficiency by total days `r e[[1]]`

Efficiency per run day `r e[[2]]`


### After switch to single-shot standards

```{r}
e <- effdate("2018-05-01", "2019-12-16")
```

Efficiency by total days `r e[[1]]`

Efficiency per run day `r e[[2]]`

# Efficiency of client sample production
